---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# nossaflex

<!-- badges: start -->
[![R-CMD-check](https://github.com/AlbanSagouis/nossaflex/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/AlbanSagouis/nossaflex/actions/workflows/R-CMD-check.yaml)
<!-- badges: end -->

The nossaflex package is the entry of the NOSSAFLEX file naming convention into the R
universe to help scientific, professional or amateur photographers to name their
picture files consistently and informatively.

When taking a picture with an analog camera, data such as aperture, shutter speed
or focal length are not automatically saved the way they are in a digital camera.
Many photographers write down these precious metadata in a notebook, we want to
help them improve their workflow and data quality. 

## What is NOSSAFLEX?
Here is an explanation from the creators:

> It’s as easy as the name – NOSSAFLEX has all of the information in the title.
>
> NO = Number  
> SS = Shutter Speed  
> A  = Aperture  
> FL = Focal Length  
> EX = Exposure  

NOSSAFLEX file names looks like this: `NO03_SS250_A8_FL80_EX0.jpg` or this:
`NO34_SS30_A2.8_FL35_EX+1.tiff`!

Learn more on their [website]{https://nossaflex.io/the-system} or on their
[Youtube channel]{https://www.youtube.com/@NOSSAFLEX}.

## The package
Here are the two main functions in the package:

- `renaming_nossaflex` batch-renames picture files from uninformative `DSC_00345.jpg`
 to information-rich NOSSAFLEX name based on data provided by the user, see {analog}
 section: `NO03_SS250_A8_FL80_EX0.jpg`.
- `editing_exif` batch-saves the metadata of the pictures into the exif slots of
the scan files (jpg, tiff, etc).

## Analog or an other app

## The workflow


## Installation

You can install the development version of nossaflex from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
# devtools::install_github("AlbanSagouis/nossaflex")
```

## Example

This is a basic example which shows you how to solve a common problem:

```{r renaming, eval = FALSE}
library(nossaflex)
files <- c("Pictures/2024/01 02 Winter in Berlin/DSC_001034",
           "Pictures/2024/01 02 Winter in Berlin/DSC_001035",
           "Pictures/2024/01 02 Winter in Berlin/DSC_001036")
filenames <- reading_nossaflex(path = "path_to_the_filenames.txt") # provided by the `analog` app
renaming_nossaflex(filenames = filenames, files = files)
```

Additionally you may want to safely save the shots metadata inside the scan files:

```{r exif_editing, eval = FALSE}
metadata <- reading_nossaflex(path = "path_to_the_filenames.txt") |>  # provided by the `analog` app
     parsing_nossaflex()
editing_exif(files, metadata)
```


## Related work
The package relies heavily on the great `exiftoolr`{https://github.com/JoshOBrien/exiftoolr/}
package by @JoshOBrien which itself depends on the great `exiftool`{https://exiftool.org/}
software by Phil Harvey.  
Finally, jExifToolGUI{https://github.com/hvdwolf/jExifToolGUI} offers exif 
editing and with a Graphical Interface, nice.
